### 2025-03-25 notes/ms.tex
update

\begin{claim}\leavevmode
Any Riemannian surface \((\Sigma,g)\) has local isothermic coordinates. (In fact, for every power series we get another isothermic coordinates. There is a group action of the \textit{\textbf{local biholomorphisms}}. In higher dimension this is only finite dimensional, generated by inversions (this is a group, like inversion about circle in \(\mathbb{C}\) and isometries (i.e. \(\operatorname{Isom}(\mathbb{R}^n) \supset\mathsf{O}(n),\mathbb{R}^n\)). So conclusion: in dimension 2 it has to do with complex analysis and in higher dimension it's just different.)
\end{claim}

@@

\begin{defn}\leavevmode
\(V\) has \textit{\textbf{vectors}}. \(V^\vee\) has \textit{\textbf{covectors}}.  \(\Lambda^{2}V\) has \textit{\textbf{bivectors}}.  \(\Lambda^{3}V\) \textit{\textbf{trivectors}}.  \textit{\textbf{Polyvectors}}. For bundles:  \(\Lambda^{2}T_M\) \textit{\textbf{bivector fields}}.  \(\Lambda^{m}T_M\) \textit{\textbf{polyvector (or multivector) fields}}, they are dual to  \(\Omega^{m}=\Lambda^{m}\Omega\), differential \(m\)-forms.
\end{defn}
For a subspace \(U \subset V\) we get corresponding \(\underbrace{\Lambda^{m}U }_{\substack{\text{1-dim casr}  \\ \cong\mathbb{R}}}\xrightarrow{\Lambda^{m}j}\Lambda^{m}V\)
and corresponidingly
\[\underbrace{\mathbb{P}\Lambda^{m}U}_{\substack{\text{1 dim}  \\ =pt}}\xrightarrow{\mathbb{P}(\Lambda^{m}j)}\mathbb{P}\Lambda^{m}U\]

@@

Now do
\[\begin{tikzcd}0\arrow[r]&U^{(m)}\arrow[r]&V^{(n)}\arrow[r]&Q^{(n-m)}\arrow[r]&0\end{tikzcd}\]
dualize
\[\begin{tikzcd}0\arrow[r]&Q^\vee\arrow[r]&V^\vee\arrow[r]&U^\vee\arrow[r]&0\end{tikzcd}\]
So you automatically get isomorfphism
\[\operatorname{Gr}(m,V)=\operatorname{Gr}(V,n-m)=\operatorname{Gr}(n-m,V^\vee)=\operatorname{Gr}(V^\vee,m)\]
And now pick some orientation on \(V\), you shall get 
\begin{exercise}\leavevmode
\(\Lambda^{n}V \cong \Lambda^{m}U \otimes \Lambda^{n-m}Q\)
\end{exercise}

@@

\subsection{ Now}
Consider 
\[M^{(m)}\xrightarrow{f}N^{(2)}\]
and do
\[\mathbb{R}^m \cong T_p^m M \xrightarrow{d_pf}T_{f(p)}N \cong \mathbb{R}^n\]
so for every regular (=rank is \(m\)=the map is an embedding=the thing is a subvariety) \(p\) you get a point in grassmanian
\[\operatorname{Gr}(m,T_{f(p)}N)\]
Consider \(f^*T_N\) which is a vector bundle over \(M\), then we can consider
\[(df):T^{(m)}_M \overset{\text{by regularity,} }{\hookrightarrow } f^*T^{(n)}_N \to \underbrace{f^*(T_N / df(T_M))^{n-m}}_{\text{\textit{\textbf{normal bundle}}} }\]
and then consider the \textit{\textbf{Grassmanization}} of \(f^*T_N\), which is a bundle
\[\begin{tikzcd}
\operatorname{Gr}(m,f^*T_N)\arrow[d]\\
M
\end{tikzcd}\]
Now consider sections of this thing.

\begin{thing7}{Important observation}\leavevmode
 Given a trivialization of \(f^*T_N\), a section of the thing becomes just a map
 \[M \to \operatorname{Gr}(m,n)\]
 (Because a section of a trivial bundle is just a map to the fiber.) 
\end{thing7}

@@

Put a surface in \(\mathbb{R}^3\). Basis for tangent space is
\[(x_u,y_u,z_u), (x_v,y_v,z_v)\]
So basis for projectivization is
\[(y_uz_u-y_vz_u, x_uz_v-x_vz_u,x_uy_v,x_vy_u)\]
and in general, when you get
\begin{align*}
\Sigma&\to \mathbb{R}^n\\
\frac{\partial }{\partial u}x, \frac{\partial }{\partial v}X &\rightsquigarrow \frac{\partial x}{\partial u}\wedge \frac{\partial x}{\partial v}
\end{align*}
\begin{thing8}{Lesson}\leavevmode
Plücker coordinates of oriented Grassmanian are the same as coordinates of normal bundle!
\end{thing8}
But also notice that you can write
\[\{x^i,x^j\}_{du \wedge dv}\]
And the point of all this is that

@@

\begin{thing6}{Reminder of the end of last lecture}[Variation of the tangent direction]\leavevmode
	\begin{align*}V'(t=0)[\underbrace{\delta \varphi}_{:=w}]= \int_{\Sigma}\frac{z_x\cdot w_x+z_y\cdot w_y}{\sqrt{g} }dudv\\
		&=\int \left<\delta \varphi,\text{something} \right>\frac{\sqrt{g} dudv}{\text{volume form} }
	\end{align*}
where \(\delta \varphi\) is a section of \(f^* T_{\mathbb{R}^n}=df(T_M) \oplus^\perp N\). And \textbf{something} is a unique thing that exists making the equality hold. This is a possible definition of \textit{\textbf{mean curvature vector}} \(\vec{H} \in N\).

And you can also write
\[\int dv \wedge \left(\frac{z_u}{\sqrt{g} \cdot w_u du}\right) = \int dv \wedge \left(\frac{z_u}{\sqrt{g} }dw\right) \]
where \(dw=w_u du+\ldots+dv\). And now we want to integrate by parts so if you recall
\[=-\int w \cdot \partia\left(\frac{z_u}{v_g}dv\right) \]
So the integral above becomes
\begin{align*}
\int_{\Sigma}\frac{z_x\cdot w_x+z_y\cdot w_y}{\sqrt{g} }dudv&=-\int \left(\partial_u \left(\frac{z_u}{\sqrt{g} }\right)+\left(\partial_v \frac{z_v}{\sqrt{g} } \right) \cdot w du dv
\end{align*}
so if that is zero for all \(w\).
\end{thing6}

Right so that is the \textit{\textbf{first variation of volume}}? It's
\[V'|_{t=0}=-\int_\Sigma(\sqrt{g} du) \left<H,W\right>\]
And it has all to do with the expression \(\Sigma g^{ij}B_{ij}\).

>>>>

\begin{claim}\leavevmode
Any Riemannian surface \((\Sigma,g)\) has local isothermic coordinates. (In fact, for every power series we get another isothermic coordinates. There is a group action of the \textit{\textbf{local biholomorphisms}}. In higher dimension this is only finite dimensional, generated by inversions (this is a group, like inversion about circle in \(\mathbb{C}\)) and isometries (i.e. \(\operatorname{Isom}(\mathbb{R}^n) \supset\mathsf{O}(n),\mathbb{R}^n\)). So conclusion: in dimension 2 it has to do with complex analysis and in higher dimension it's just different.)
\end{claim}

@@

\begin{defn}\leavevmode
\(V\) has \textit{\textbf{vectors}}. \(V^\vee\) has \textit{\textbf{covectors}}.  \(\Lambda^{2}V\) has \textit{\textbf{bivectors}}.  \(\Lambda^{3}V\) \textit{\textbf{trivectors}}.  \textit{\textbf{Polyvectors}}. For bundles:  \(\Lambda^{2}T_M\) \textit{\textbf{bivector fields}}.  \(\Lambda^{m}T_M\) \textit{\textbf{polyvector (or multivector) fields}}, they are dual to  \(\Omega^{m}=\Lambda^{m}\Omega\), differential \(m\)-forms.
\end{defn}
For a subspace \(U \subset V\) we get corresponding \(\underbrace{\Lambda^{m}U }_{\substack{\text{1-dim case}  \\ \cong\mathbb{R}}}\xrightarrow{\Lambda^{m}j}\Lambda^{m}V\)
and corresponidingly
\[\underbrace{\mathbb{P}\Lambda^{m}U}_{\substack{\text{1 dim}  \\ =pt}}\xrightarrow{\mathbb{P}(\Lambda^{m}j)}\mathbb{P}\Lambda^{m}U\]

@@

Now do
\[\begin{tikzcd}0\arrow[r]&U^{(m)}\arrow[r]&V^{(n)}\arrow[r]&Q^{(n-m)}\arrow[r]&0\end{tikzcd}\]
dualize
\[\begin{tikzcd}0\arrow[r]&Q^\vee\arrow[r]&V^\vee\arrow[r]&U^\vee\arrow[r]&0\end{tikzcd}\]
So you automatically get isomorphisms
\[\operatorname{Gr}(m,V)=\operatorname{Gr}(V,n-m)=\operatorname{Gr}(n-m,V^\vee)=\operatorname{Gr}(V^\vee,m)\]
And now pick some orientation on \(V\), you shall get 
\begin{exercise}\leavevmode
\(\Lambda^{n}V \cong \Lambda^{m}U \otimes \Lambda^{n-m}Q\)
\end{exercise}

@@

\subsection{Gauss map}
Consider 
\[M^{(m)}\xrightarrow{f}N^{(2)}\]
and do
\[\mathbb{R}^m \cong T_p^m M \xrightarrow{d_pf}T_{f(p)}N \cong \mathbb{R}^n\]
so for every regular (=rank is \(m\)=the map is an embedding=the thing is a subvariety) \(p\) you get a point in grassmanian
\[\operatorname{Gr}(m,T_{f(p)}N)\]
Consider \(f^*T_N\) which is a vector bundle over \(M\), then we can consider
\[(df):T^{(m)}_M \overset{\text{by regularity,} }{\hookrightarrow } f^*T^{(n)}_N \to \underbrace{f^*(T_N / df(T_M))^{(n-m)}}_{\text{\textit{\textbf{normal bundle}}} }\]
and then consider the \textit{\textbf{Grassmanization}} of \(f^*T_N\), which is a bundle
\[\begin{tikzcd}
\operatorname{Gr}(m,f^*T_N)\arrow[d]\\
M
\end{tikzcd}\]
Now consider sections of this thing.

\begin{thing7}{Important observation}[Gauss map definition]\leavevmode
 Given a trivialization of \(f^*T_N\), a section of the thing becomes just a map
 \[M \to \operatorname{Gr}(m,n)\]
 (Because a section of a trivial bundle is just a map to the fiber.) 
\end{thing7}

@@

Put a surface in \(\mathbb{R}^3\). Basis for tangent space is
\[(x_u,y_u,z_u), (x_v,y_v,z_v)\]
So basis for projectivization is
\[(y_uz_u-y_vz_u, x_uz_v-x_vz_u,x_uy_v,x_vy_u)\]
and in general, when you get
\begin{align*}
\Sigma&\to \mathbb{R}^n\\
\frac{\partial x}{\partial u}, \frac{\partial x}{\partial v} &\rightsquigarrow \frac{\partial x}{\partial u}\wedge \frac{\partial x}{\partial v}
\end{align*}
\begin{thing8}{Lesson}\leavevmode
Plücker coordinates of oriented Grassmanian are the same as coordinates of normal bundle!
\end{thing8}
But also notice that you can write
\[\{x^i,x^j\}_{du \wedge dv}\]
And the point of all this is that

@@

\subsection{Reminder: variational approach}

\begin{thing6}{Reminder of the end of last lecture}[Variation of the tangent direction]\leavevmode
	\begin{align*}V'(t=0)[\underbrace{\delta \varphi}_{:=w}]&= \int_{\Sigma}\frac{z_x\cdot w_x+z_y\cdot w_y}{\sqrt{g} }dudv\\
		&=\int \left<\delta \varphi,\text{something} \right>\frac{\sqrt{g} dudv}{\text{volume form} }
	\end{align*}
where \(\delta \varphi\) is a section of \(f^* T_{\mathbb{R}^n}=df(T_M) \oplus^\perp N\). And \textbf{something} is a unique thing that exists making the equality hold. This is a possible definition of \textit{\textbf{mean curvature vector}} \(\vec{H} \in N\).

And you can also write
\[\int dv \wedge \left(\frac{z_u}{\sqrt{g} \cdot w_u du}\right) = \int dv \wedge \left(\frac{z_u}{\sqrt{g} }dw\right) \]
where \(dw=w_u du+\ldots+dv\). And now we want to integrate by parts to get
\[=-\int w \cdot \partial\left(\frac{z_u}{v_g}dv\right) \]
So the integral above (with the \textbf{something} inside) becomes
\begin{align*}
\int_{\Sigma}\frac{z_x\cdot w_x+z_y\cdot w_y}{\sqrt{g} }dudv&=-\int \left(\partial_u \frac{z_u}{\sqrt{g}}+\partial_v \frac{z_v}{\sqrt{g}}  \right)\cdot w du dv
\end{align*}
so if that is zero for all \(w\), then the thing in parenthesis must be zero by nondegeneracy of metric.
\end{thing6}

Right so what is the \textit{\textbf{first variation of volume}}? It's
\[V'|_{t=0}=-\int_\Sigma(\sqrt{g} du) \left<H,W\right>\]
And it has all to do with the expression \(\Sigma g^{ij}B_{ij}\).
